---
title: "p8105_hw1_yh2736"
author: "Yongmei Huang"
date: "9/20/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

set.seed(500)

```


# question 1
##  code chunk1: create a data frame
```{r, echo = TRUE}
# dataset of question 1 ques1_data_set including 4 variable: random sample, logical vector, character vector
# and factor vector

ques1_data_set = tibble(
  rand_size8_sd = rnorm(8),    # random sample
  log_vect = rand_size8_sd > 0, # logical vector
  char_vect_len8 = c("male", "female", "male", "male", "female", "male", "male", "female"),  # character vector
  fac_len8_lev3 = factor(c("low", "high", "middle", "middle", "low", "low", "high", "middle")) # factor vector
)



```

* the mean of variable 1
the mean of variable rand_size8_sd of dataset is `r mean(ques1_data_set$rand_size8_sd)`;

* the mean of variable 2
the mean of variable log_vect of dataset is `r mean(ques1_data_set$log_vect)`;

* the mean of variable 3
the mean of variable char_vect_len8 of dataset is `r mean(ques1_data_set$char_vect_len8)`;

* the mean of variable 4
the mean of variable fac_len8_lev3 of dataset is `r mean(ques1_data_set$fac_len8_lev3)`;

##  code chunk2: variable convert
```{r, echo = TRUE}
# convert the logical vector to numeric, and multiply the random samble by the resule
rand_mul_numeric_of_log = ques1_data_set$rand_size8_sd * as.numeric(ques1_data_set$log_vect)

# convert the logical vector to factor, and multiply the random samble by the resule
rand_mul_factor_of_log = ques1_data_set$rand_size8_sd * as.factor(ques1_data_set$log_vect)


# convert the logical vector to factor,and then convert the result to numberic, 
# and multiply the random samble by the resule
rand_mul_numeric_of_factor_of_log = ques1_data_set$rand_size8_sd * as.numeric(as.factor(ques1_data_set$log_vect))

```

* convert the logical vector to numeric, and multiply the random samble by the resule,
  output is `r rand_mul_numeric_of_log`

* convert the logical vector to factor, and multiply the random samble by the resule,
  output is `r rand_mul_factor_of_log`


* convert the logical vector to factor,and then convert the result to numberic, 
  and multiply the random samble by the resule. output is `r rand_mul_numeric_of_factor_of_log`
  
# question 2
## chunk 1: setup data frame
```{r, echo = TRUE}
## data frame with 5 variable
ques2_data_set = tibble(
  x = rnorm(500),   # random sample of size 500 from a standard normal distribution
  y = rnorm(500),   # random sample of size 500 from a standard normal distribution
  log_vect_larger_than_one = (x + y) > 1,   #logical vector indicating which X+y>1
  num_vect = as.numeric(log_vect_larger_than_one),   # A numeric vector created by coercing the above logical vector
  fact_vect = as.factor(log_vect_larger_than_one)    # A factir vector crated by coercing the above logical vector
)

```

* THe size of dataset is `r nrow(ques2_data_set) * ncol(ques2_data_set)`
