---
title: "p8105_hw1_yh2736"
author: "Yongmei Huang"
date: "9/20/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

```


# question 1, create a data frame
```{r, echo = TRUE}
# dataset of question 1 ques1_data_set including 4 variable: random sample, logical vector, character vector
# and factor vector

ques1_data_set = tibble(
  rand_size8_sd = rnorm(8),    # random sample
  log_vect = rand_size8_sd > 0, # logical vector
  char_vect_len8 = c("male", "female", "male", "male", "female", "male", "male", "female"),  # character vector
  fac_len8_lev3 = factor(c("low", "high", "middle", "middle", "low", "low", "high", "middle")) # factor vector
)



```

* the mean of variable 1
the mean of variable rand_size8_sd of dataset is `r mean(ques1_data_set$rand_size8_sd)`;

* the mean of variable 2
the mean of variable log_vect of dataset is `r mean(ques1_data_set$log_vect)`;

* the mean of variable 3
the mean of variable char_vect_len8 of dataset is `r mean(ques1_data_set$char_vect_len8)`;

* the mean of variable 4
the mean of variable fac_len8_lev3 of dataset is `r mean(ques1_data_set$fac_len8_lev3)`;

